\documentclass[letterpaper,12pt]{article}
\usepackage{amsmath, amsthm, amssymb, geometry}
\geometry{margin=1in}

\newtheorem{theorem}{Theorem} % Define the theorem environment

\documentclass[letterpaper,12pt]{article}
\usepackage{amsmath, amssymb, geometry}
\geometry{margin=1in}
\title{The Unified Theory of Relativity: Dimensional Recursion, Time, and Energy}
\author{Michael Vera}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper dismantles Einstein’s Theory of Relativity by illustrating that it imposes a D=6 concept of time onto a D=2 mathematical framework, neglecting the recursive nature of dimensional surface interactions. The Unified Theory of Energy (UTE) redefines time as a synthetic construct that emerges only at D=6, challenging classical assumptions. By applying dimensional derivatives and recursive Newtonian gravitation, we establish a more coherent understanding of time, scale, and energy transitions across dimensions.
\end{abstract}

\section{Introduction}
The Theory of Relativity’s fatal flaw is its forced application of time—a D=6 construct—into D=2 mathematics, denying the dimensional recursion essential for accurate physical modeling. The UTE reveals that time does not exist below D=6, highlighting the inadequacy of current models.

\section{Dimensional Derivatives and Recursive Time}
Accurate time calculation requires taking derivatives at each dimensional transition, with scale considerations:

\begin{equation}
    T(D) = \frac{dE}{dD} = \frac{Gm_1m_2}{r^2} \times S(D),
\end{equation}

where $S(D)$ adjusts for dimensional scale, ensuring locally valid time.

\section{Newton’s Law of Gravitation in Recursive Dimensions}
Recursive application of Newton’s Law reveals:

\begin{equation}
    G = \frac{4\pi^2r^3}{T^2},
\end{equation}

correcting time measurements from massless centers to mass-containing surfaces, and extending to radiation limits.

\section{Ozone and Earth: A Dimensional Case Study}
The orbital time of Earth around the Sun mirrors the time of an ozone electron due to dimensional recursion:

\begin{equation}
    T_{electron} = T_{Earth},
\end{equation}

proving that time scales consistently across dimensions in UTE.

\section{Conclusion}
Time, as defined by UTE, exists only at D=6, invalidating relativity’s attempts to force it into lower-dimensional math. Recognizing dimensional recursion transforms our understanding of time, energy, and mass interactions.

\end{document}
